Iris Research

### 2019-01-25 ex/ex-research.Rmd
change dataset back to the basic iris data
parameterize the research
add closing blurb

---
title: "Iris Research"
author: "Cole Arendt"
date: "1/6/2019"
output: pdf_document
---

@@

input_data <- readRDS("iris_altered.rds")

@@

```{r explore_output}
knitr::kable(all_detail_tall)
```

>>>>

---
title: "Iris Research"
author: "Cole Arendt"
date: "1/6/2019"
output: pdf_document
params:
  input_data: "iris.rds"
---

@@

input_data <- readRDS(params$input_data)

@@

```{r explore_output}
by_med_sepal_length <- all_detail %>% arrange(desc(median_Sepal.Length)) %>% pull(Species)

knitr::kable(all_detail_tall)
```

Did you notice that `r by_med_sepal_length %>% .[[1]] %>% as.character()` has
the highest median Sepal.Length? And `r by_med_sepal_length %>%
.[[length(by_med_sepal_length)]] %>% as.character()` has the lowest.
